\documentclass[12pt]{article}
\usepackage{lingmacros}
\usepackage{tree-dvips}
\begin{document}
\pagenumbering{gobble}
\title{\bf{Title of Dissertation}}

\vspace*{3\baselineskip}
\centerline{\bf{Resource Allocation And Management in Cloud Computing Systems}}
\vspace*{1\baselineskip}
\centerline{A Dissertation Proposal presented}
\vspace*{1\baselineskip}
\centerline{by} 
\vspace*{1\baselineskip}
\centerline{\bf{Nhat Tan Le}}
\vspace*{1\baselineskip}
\centerline{to} 
\vspace*{1\baselineskip}
\centerline{The Graduate School}
\vspace*{1\baselineskip}
\centerline{in Partial Fulfillment of the}
\vspace*{1\baselineskip}
\centerline{Requirements}
\vspace*{1\baselineskip}
\centerline{for the Degree of}
\vspace*{1\baselineskip}
\centerline{\bf{Doctor of Philosophy}}
\vspace*{1\baselineskip}
\centerline{in}
\vspace*{1\baselineskip}
\centerline{\bf{Computer Science}}
%\vspace*{1\baselineskip}
%\centerline{\bf{(Concentration - optional)}}
\vspace*{2\baselineskip}
\centerline{Stony Brook University}
\vspace*{2\baselineskip}
\centerline{\bf{December 2018}}     

\newpage
\pagenumbering{gobble}

\vspace*{32\baselineskip}
\centerline{\it{(include this copyright page only if you are selecting copyright through ProQuest, which is optional)}}
\vspace*{1\baselineskip}
\centerline{Copyright by}
\centerline{Nhat Tan Le}
\centerline{2017}

\newpage
\pagenumbering{roman}
\setcounter{page}{2}

\centerline{\bf{Stony Brook University}}
\vspace*{1\baselineskip}
\centerline{The Graduate School}
\vspace*{2\baselineskip}
\centerline{Your Name}
\vspace*{2\baselineskip}
\centerline{We, the dissertation committe for the above candidate for the}
\vspace*{1\baselineskip}
\centerline{Doctor of Philosophy degree, hereby recommend}
\vspace*{1\baselineskip}
\centerline{acceptance of this dissertation}
\vspace*{2\baselineskip}
\centerline{\bf{Zhenhua Liu}}
\centerline{\bf{Assistant Professor, AMS \& CS}}
\vspace*{2\baselineskip}
\centerline{\bf{Name - Chairperson of Defense}}
\centerline{\bf{Include title and department}}
\vspace*{2\baselineskip}
\centerline{\bf{Type the remaining committe members using the above format. Type each member's}}
\centerline{\bf{name, title and department. Always make sure the signature page is kept to one page in}} 
\centerline{\bf{length.}}
\vspace*{1\baselineskip}
\centerline{\bf{Type the outside member's name last. Include discipline and affiliation.}}
\vspace*{2\baselineskip}
\centerline{This dissertation is accepted by the Graduate School}
\vspace*{3\baselineskip}
\centerline{Dean of the Graduate School}

\newpage

\centerline{Abstract of the Dissertation}
\vspace*{1\baselineskip}
\centerline{\bf{Title of Dissertation}}
\vspace*{1\baselineskip}
\centerline{by}
\vspace*{1\baselineskip}
\centerline{\bf{Your Name}}
\vspace*{1\baselineskip}
\centerline{\bf{Doctor of Philosophy}}
\vspace*{1\baselineskip}
\centerline{in}
\vspace*{1\baselineskip}
\centerline{\bf{Full Name of Degree Program}}
\vspace*{1\baselineskip}
\centerline{\bf{(Concentration - optional)}}
\vspace*{1\baselineskip}
\centerline{Stony Brook University}
\vspace*{1\baselineskip}
\centerline{\bf{2017}}
\vspace*{2\baselineskip}
Begin typing abstract here.

\newpage
\centerline{\bf{Dedication Page}}
\vspace*{4\baselineskip}
This page is optional.

\newpage
\centerline{\bf{Frontispiece}}
\vspace*{4\baselineskip}
The frontispiece is generally an illustration, and is an optional page.

\newpage
\centerline{\bf{Table of Contents}}

\newpage
\centerline{\bf{List of Figures/Tables/Illustrations}}
\vspace*{4\baselineskip}
Include these lists if applicable - if you have a list for each, each list must begin on a new page.

\newpage
\centerline{\bf{List of Abbreviations}}
\vspace*{4\baselineskip}
Include this list if applicable.

\newpage
\centerline{\bf{Preface}}
\vspace*{4\baselineskip}
This page is optional.

\newpage
\centerline{\bf{Acknowledgements}}
\vspace*{4\baselineskip}
This page is optional.

\newpage
\centerline{\bf{Vita, Publications and/or Fields of Study}}
\vspace*{4\baselineskip}
This page is optional for doctoral students only.

\newpage
\pagenumbering{arabic}


\centerline{\bf{Chapter 1}}


\end{document}