\textbf{Submission Guidelines}: Papers should not exceed \textbf{12 pages} double column including figures, tables in standard ACM format excluding references. In addition, authors may supplement their paper with an appendix with unspecified length for the sole purpose of justifying the technical correctness of their claims stated in the body (technical part of a long proof to be self-contained, additional experimental validation). \textbf{The appendix does not count towards the original 12 pages}. Papers must be submitted electronically in printable pdf form. Templates for the standard ACM format can be found at this link. Both strict and alternate styles are acceptable for submission. No changes to margins, spacing, or font sizes are allowed from those specified by the style files. Papers violating the formatting guidelines will be returned without review.

All submissions will be reviewed using a double-blind review process. The identity of authors and referees will not be revealed to each other. To ensure blind reviewing, authors names and affiliations should not appear in the paper; bibliographic references should be made in such a way as to preserve author anonymity. Accepted papers will appear in the conference proceedings published on ACM Performance Evaluation Review.

Important Dates: (Deadlines are at 11:59:59 p.m. EST on the dates indicated.)

Fall: Registration of abstract: October 11, 2016; Paper submission, October 18, 2016.

Winter: Registration of abstract: Jan. 10, 2017; Paper submission: January 17, 2017.

Paper notification: TBD

Camera ready submission: April 7, 2017

Conference: June 5-9, 2017
